\documentclass[12pt,overlapped,line]{res}
%\documentstyle[margin, line]{res}


\usepackage{url}
%for funny lists
\usepackage{pifont}
\usepackage{multicol}
\usepackage{pstricks,pst-node,pst-text,pst-3d}
\usepackage{amsmath}
\usepackage{pslatex}

% \usepackage{pstricks,tabularx,paralist}
% \usepackage{pst-barcode}

\usepackage[dvips]{graphicx}
%\usepackage[usenames,dvipsnames]{color}
\usepackage[]{hyperref}

% useful for control of listings
\usepackage{enumitem}

\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
\newcommand{\mplace}[1]{\textbf{#1}}
\newcommand{\wdescription}[1]{({\small \textit{#1}})}
\newcommand{\mtitle}[1]{``#1''}
\newcommand{\mauthors}[1]{ \textit{#1.}}
\newcommand{\mwhere}[1]{#1.}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=7.0in

\begin{document}
\name{Yaroslav O. Halchenko}

\address{
  \textbf{Mailing Address: }\newline
  \ PBS Department, Dartmouth\\
  419 Moore Hall\\
  Hinman Box 6207\\
  Hanover, NH 03755 USA \newline
}

%%\address{
%%   \textbf{Current Address: }\newline
%%   206 Van Buren Str., Apt.3 \\
%%   Newark NJ, 07105 \\
%%   USA
%%}
\address{
 \textbf{Internet Addresses:}\newline
  \ \href{URL}{career@onerussian.com}\\
  \href{URL}{http://www.onerussian.com}\\
  \href{URL}{http://www.linkedin.com/in/yarik}
%  \href{URL}{http://neurotree.org/neurotree/tree.php?pid=23884
%  \texttt{+1 [973] 353-5440 x263}\\}
}


% \address{
%  \textbf{GnuPG Key:}\newline
%  \ 75C024C8, \url{http://www.onerussian.com/gpg-yoh.asc}\ \\
%  \wdescription{FP: 3BB6 E124 0643 A615 6F00 6854 8D11 4563 75C0 24C8}
% }

\begin{resume}
% \vspace{-2.15em}
%  \small{\begin{flushright}%\hspace{7.48em}
% \textbf{GnuPG Key:} \ 75C024C8, \url{http://www.onerussian.com/gpg-yoh.asc}
% \end{flushright}
%  \vspace{-2.6em}
%  \begin{flushright}
%    \hspace{7.7em}\textbf{Fingerprint:}
%    \ 3BB6 E124 0643 A615 6F00 6854 8D11 4563 75C0 24C8
% \end{flushright}
%}

% %_________________________________________________________________
% \section{Objective}



% To combine theoretical knowledge (mathematics, physics, numeric
% methods, etc) and computer skills (programming, system administration,
% design) to produce useful ideas and results.

%_________________________________________________________________
\section{Education}
\begin{format}
  \title{l}\dates{r}\\
  \employer{l}\location{r}\\
  \body\\
\end{format}

\employer{Computer Science Dept,\\ NJIT (NJ Institute of Technology)}
\title{Ph.D. student. GPA 4.00}
\location{Newark NJ, USA}
\dates{January 2003 -- May 2009}
\begin{position}
  PhD degree in Computer Science awarded in May 2009.
\end{position}

 \employer{Computer Science Dept,\\ UNM (University of New Mexico)}
 \title{MS student. GPA 4.00}
 \location{Albuquerque NM, USA}
 \dates{January 2000 -- December 2003}
 \begin{position}
  MS degree in Computer Science after successfully passing MS
 qualification examination in August 2003.
 \end{position}

 \employer{Computer Systems Dept,\\
   VSTU (Vinnytsia State Technical University)}
 \title{Graduate student}
 \location{Vinnytsia, Ukraine}
 \dates{1998 -- 1999}
 \begin{position}
  Master`s degree in Laser and Optoelectronic Engineering.
 \end{position}

 \employer{Computer Systems Dept,\\ VSTU}
%\ \url{http://www.vstu.edu.ua/}}
 \title{Student}
 \location{Vinnytsia, Ukraine}
 \dates{1994 -- 1998}
 \begin{position}
  Bachelor's degree in Laser and Optoelectronic Engineering with
  honors.
 %, com Lauder.
 \end{position}

 \employer{Physical and Mathematical Gymnasia\\ No.17}
 \title{High School Student}
 \location{Vinnytsia, Ukraine}
 \dates{1992 -- 1994}
 \begin{position}
  Graduated with honors.
 \end{position}

 \employer{Physical and Mathematical Correspondence School}
 \title{High School Student}
 \location{Moscow Physical Engineering Institute}
 \dates{1991 -- 1994}
 \begin{position}
 \vspace{-2.5em}
 \end{position}

 \employer{Aerospace Correspondence School ``Soyuz''}
 \title{High School Student}
 \location{Moscow Physical Engineering Institute}
 \dates{1991 -- 1992}
 \begin{position}
 \end{position}

\vspace{-3em}
%_________________________________________________________________
 \section{Work Experience}
 \begin{format}
   \title{l}\dates{r}\\
   \employer{l}\location{r}\\
   \body\\
 \end{format}


\employer{Dept of Psychological and Brain Sciences,\\ Dartmouth College}
\title{Postdoctoral Fellow}
\location{Hanover NH, USA}
\dates{May 2009 -- present}
\begin{position}
  Working with Dr. James V. Haxby.  Projects: visual objects
  processing, multimodal and multivariate analysis for functional
  neural data: \url{http://www.pymvpa.org}, software deployment and
  reproducibility in cognitive neuroscience:
  \url{http://neuro.debian.net}.
\end{position}

 \employer{Mind/Brain RUMBA Laboratory\\\url{http://www.rumba.rutgers.edu}}
 \title{Research Assistant}
 \location{Psych. Department, Rutgers-Newark NJ., USA}
 \dates{August 2002 -- May 2009}
 \begin{position}
   Projects:\\
%   \begin{itemize}
   - Predictive decoding of the neural data from different imaging
     modalities (e.g. EEG, fMRI) to gain better understanding of
     perception (e.g. auditory) and cognitive (e.g. category specific
     processing) neuroscientific problems \\
   - Graphical modeling of functional brain organization \\
   - Fusion of multiple functional brain imaging modalities
     (f{MRI}/{EEG}) to gain better understanding and localization of
     underlying neural activity
%    brain imaging projects such as ``brain reading''
%    (application of the classifiers on categorical data), graphical
%    modeling (Structural Equation Modeling), and fusion of multiple
%    functional brain imaging modalities (f{MRI}/{EEG}) to obtain higher
%    spatial/temporal resolution mapping of brain activity.
 \end{position}

% \newpage

 \employer{Open Source Community (Debian GNU/Linux) \url{http://www.debian.org}}
 \title{Debian Developer}
 \location{}
 \dates{December 2005 -- present}
 \begin{position}
   Packaging and maintenance of FOSS software within the Debian GNU/Linux OS.
 \end{position}

 \employer{Rutgers-Newark}
 \title{GNU/Linux Cluster System Administrator}
 \location{Psych. Department, Rutgers-Newark NJ., USA}
 \dates{September 2005 -- May 2009}
 \begin{position}
   Deployment and maintenance of 27 node high availability {AMD}
   {O}pteron based cluster. % running GNU/Linux Debian OS.
 \end{position}

 \employer{Brain and Computation Laboratory \url{http://www-bcl.cs.unm.edu}}
 \title{Research Assistant}
 \location{CS Dept., UNM Albuquerque NM, USA}
 \dates{June 2000 -- July 2002}
 \begin{position}
   Have been working  on deploying ICA (Independent Component
   Analysis) techniques in processing of MEG (Magnetoencephalography)
   data which are part of the DreamMon project.

 %  Maintaining computer park in the lab running linux GNU Debian 2.x.

 \end{position}

 \employer{CS Dept., UNM}
 \title{Teaching Assistant}
 \location{Albuquerque NM, USA}
 \dates{January 2000 -- May 2000}
 \begin{position}
   Teaching Assistant for ``Intermediate Programming'' (CS251) class
   with Prof. David Ackley (CS Department, UNM).
 \end{position}


 \employer{VSTU}
 \title{Research Assistant}
 \location{Vinnitsya, Ukraine}
 \dates{ 1993 -- 1997 }
 \begin{position}
 Part-time designer and software developer of the system for
 diagnostics of mobile segments in vertebral column, which later was
 utilized in national hospitals of Ukraine.
 \end{position}

 \employer{Liana Company}
 \title{Software Developer}
 \location{Vinnitsya, Ukraine}
 \dates{ April 1996 -- October 1997 }
 \begin{position}
 Part-time software developer of automated system in
 Planned-Economic Department of Vinnytsia Chemical Plant (Himprom).
 \end{position}

 \section{Scholarship Awards}
 \begin{format}
   \employer{l}
   \dates{r}\\
   \body\\
 \end{format}

 \employer{}
 \dates{ 1998-1999 }
 \begin{position}
  The International Scientific Fund Representatives in Ukrainian Studentship Award.
 \end{position}

 \employer{}
 \dates{ 1995-1996 }
 \begin{position}
  The International Soros Science Educational Program (ISSEP) Studentship Award.
 \end{position}

%\newpage
 \section{Main Awards and Honors}
 \begin{format}
   \employer{l} \dates{r}\\
   \body\\
 \end{format}

 \employer{Ukraine}
 \dates{ 1996 }
 \begin{position}
   The Academy of Sciences of Ukraine \mplace{awarded the work}
   ``Information-Measuring System With Optical Transformation
   Biomedical Information''.
 \end{position}

 \employer{Bucharest, Romania}
 \dates{ October 1995 }
 \begin{position}
   \mplace{6th place} in ACM South-Eastern European Regional
   Programming Contest. \mplace{1st place} at VSTU.
 \end{position}

 \employer{Kharkiv, Ukraine}
 \dates{ April 1995 }
 \begin{position}
   \mplace{4th place} in Physics Olympiad among Colleges and
   Universities of Ukraine. \mplace{1st place} at VSTU.
 \end{position}

 \employer{ Vinnitsya, Ukraine }
 \dates{ 1994 }
 \begin{position}
 \mplace{1st place} in the Regional Contest for Programming.
 \end{position}

 \employer{ Ukraine }
 \dates{ 1994 }
 \begin{position}
   \mplace{1st place} in Competition among teenagers for the best
   computer program. Became a \mplace{Member of the Ukraine Small Academy
     of Sciences}.
 \end{position}

 \employer{Vinnitsya, Ukraine}
 \dates{ 1993 }
 \begin{position}
   \mplace{1st place} for the best solution of physical and mathematical
   problems in the competition organized by Moscow Physical Engineering Institute.
 \end{position}

 \employer{Vinnitsya, Ukraine}
 \dates{ 1993 }
 \begin{position}
   \mplace{3rd place} in the Regional Physics Olympiad.

 \end{position}

 \section{Projects and Contributions}

 \begin{itemize}[parsep=0.2em,leftmargin=1em]

 \item Cofounder and core developer of NeuroDebian project: \url{http://neuro.debian.net}

 \item Cofounder and core developer of PyMVPA (Python Multivariate Pattern Analysis): \url{http://www.pymvpa.org}

 \item Contributor to various FOSS projects: \url{http://www.ohloh.net/accounts/yarikoptic}

 \item Debian developer overseeing dozens of packages
   (\url{http://qa.debian.org/developer.php?login=yoh}) and
   participating in Debian Science and Debian Med projects.

 \end{itemize}

 \section{Skills}
  \begin{description}[parsep=0.2em,leftmargin=1em]

    \item[Programming:]\hspace*{\fill}
      \begin{itemize}
      \item More than 10 years of experience with software development
        under Linux OS: C/\Cplusplus(g++), Python, bash/awk/sed,
        CVS/SVN/git, gdb/pydb/bashdb/ddd, valgrind, gprof, etc.

      \item Past (1992-2000) working experience in software
        development on MS DOS, Windows 3.x and Windows 9x platforms:
        Turbo Pascal, VBA (Visual Basic for Applications), and Inprise
        Delphi

      \item Past (2000-2002) experience with Java (Java Swing, RMI,
        JDBC, Exemplar project:\\ \url{http://apsp.onerussian.com}),
        logic and functional languages: prolog, SML, elisp

      \item Past (2000-2004) working experience in database design:
        DBE, ODBC, Postgresql, MySQL APIs

%        \wdescription{Have written a number of small tools and a couple of
%          projects. Refer to ``Work Experience''}
%
%      \item Experienced with VBA (Visual Basic for Applications) and
%        Inprise Delphi
%
%      \item Database design. Past working experience with DBE, ODBC,
%        Postgresql, MySQL APIs

      \item Strong background in object-oriented programming methods
        and Design Patterns

      \item Experienced writer of high quality code. Coding practice
        includes thorough code reviews, detecting defects, careful
        debugging of own code and code of others, profiling,
        versioning, unit-, doc- and regression testing, and other techniques
      \end{itemize}

    \item[Administration:] \hspace*{\fill}
      \begin{itemize}

      \item Centralized systems configuration: cfengine2

      \item Linux-based (GNU Debian) network communication and
        monitoring: TCP/IP, SNMP, IPTables (shorewall), DNS (bind), NAT,
        NFS, SSH, SMTP (exim v4), Ganglia, NTop,\ etc.

      \item Web-server administration: apache/apache2
%        \wdescription{Running on
%          \url{http://www.onerussian.com}, \url{http://itanix.rutgers.edu}}

%      \item Databases: postgresql, mysql

      \item Resource management and scheduling of HP/HA computing
        clusters: torque, maui, SGE

      \item Virtualized (vserver, VirtualBox) and automated (FAI)
        deployment solutions

      \item Hardware: hardware and software RAIDs, network adapters
        and switches (interface bonding), APCs, desktop or
        rack-mounted servers; benchmarking, configuration
        optimization, maintenance and troubleshooting

      \end{itemize}

    \item[Web Design and Others:]  \hspace*{\fill}
      \begin{itemize}
      \item Basic web-designer skills: HTML, CSS, PHP%\ 
%         \wdescription{Examples
% %   home page
%           \url{http://www.onerussian.com},
% %   lab page
%           \url{http://www.rumba.rutgers.edu}
% }
      \item Strong background in graphical design and desktop
        publishing: \LaTeX\ , Inkscape, GIMP, OpenOffice.org
        % Visio, Microsoft Office etc.

      \item Excellent knowledge of mathematics and numerical methods.

      %\item Working experience with Electronic Design Automation: PCAD and
      %  Visio
      \end{itemize}

  \end{description}

 \section{Selected Publications}

 \begin{itemize}

 \item
   \mauthors{A.C.  Connolly, J.S.  Guntupalli, J. Gors, M.~Hanke,
     \textbf{Y.O.~Halchenko}, Y.C.~Wu, A.~Harve and J.V.~Haxby}
   \mtitle{Representation of biological classes in the human brain}
   \mwhere{Journal of Neuroscience, In press}

 \item
   \mauthors{K.~Gorgolewski, C.D.~Burns, C.~Madison, D.~Clark, \textbf{Y.O.~Halchenko},
     M.L.~Waskom and S.S.~Ghosh}
   \mtitle{Nipype: a flexible, lightweight and extensible neuroimaging data processing framework in Python.}
   \mwhere{Frontiers in Neuroinformatics, 2011}


 \item
   \mauthors{M.~Hanke and \textbf{Y.O.~Halchenko}}
   \mtitle{Neuroscience runs on {GNU/Linux}}
   \mwhere{Frontiers in Neuroinformatics, 2011}

 \item
   \mauthors{J.V.~Haxby, J.S.~Guntupalli, A.C.~Connolly,
     \textbf{Y.O.~Halchenko}, B.R.~Conroy, M.I.~Gobbini, M.~Hanke and
     P.J.~Ramadge}
   \mtitle{A Common, High-Dimensional Model of the Representational
     Space in Human Ventral Temporal Cortex}
   \mwhere{Neuron, 2011}

 \item
   \mauthors{M.~Hanke, \textbf{Y.O.~Halchenko}, J.V.~Haxby, S.~Pollmann}
   \mtitle{Statistical learning analysis in neuroscience: aiming for
     transparency}
   \mwhere{Frontiers in Neuroscience, 4, 2010}

 \item
   \mauthors{\textbf{Y.O.~Halchenko}, M.~Hanke}
    \mtitle{Advancing Neuroimaging Research with Predictive Multivariate
      Pattern Analysis (MVPA)}
    \mwhere{The Neuromorphic Engineer, May 2010}

 \item
   \mauthors{J.~Ramsey, S.J.~Hanson, C.~Hanson, \textbf{Y.O.~Halchenko},
     R.A.~Poldrack, C.~Glymour}
   \mtitle{Six Problems for Causal Inference from fMRI}
   \mwhere{Neuroimage, 49(2), 2010}

 \item
   \mauthors{R.A.~Poldrack, \textbf{Y.O.~Halchenko}, S.J.~Hanson}
   \mtitle{Decoding the large-scale structure of brain function by
     classifying mental states across individuals}
   \mwhere{Psychological Science, 2009}

  \item
    \mauthors{M.~Hanke, \textbf{Y.O.~Halchenko}, P.B.~Sederberg, M.~Hughes}
    \mtitle{The PyMVPA Manual}
    \mwhere{\newline Available online at \url{http://www.pymvpa.org/PyMVPA-Manual.pdf}}

 \item
   \mauthors{ M.~Hanke, \textbf{Y.O.~Halchenko}, P.B.~Sederberg, E.~Olivetti, I.~Frund, J.W.~Rieger, C.S.~Herrmann, S.J.~Hanson, S.~Pollmann}
    \mtitle{PyMVPA: a unifying approach to the analysis of neuroscientific data}
    \mwhere{Frontiers in Neuroinformatics, 3(3), 2009}

  \item
    \mauthors{M.~Hanke, \textbf{Y.O.~Halchenko}, P.B.~Sederberg, S.J.~Hanson, J.V.~Haxby, S.~Pollmann}
    \mtitle{PyMVPA: A Python toolbox for multivariate pattern analysis of fMRI data}
    \mwhere{Neuroinformatics, 7(1):37-53, March 2009}

  \item
    \mauthors{S.J.~Hanson, \textbf{Y.O.~Halchenko}}
    \mtitle{Brain reading using full brain Support Vector Machines for
      object recognition: There is no face identification area}
    \mwhere{Neural Computation, 20(2):486-503, February 2008}

  \item
    \mauthors{S.J.~Hanson, C.~Hanson, \textbf{Y.O.~Halchenko}, T.~Matsuka, A.~Zaimi}
    \mtitle{Bottom-up and top-down brain functional connectivity underlying comprehension of everyday visual action}
    \mwhere{Brain Structure and Function, 212(3-4):231-44, 2007}

  \item
    \mauthors{S.J.~Hanson, D.~Rebbechi, C.~Hanson, \textbf{Y.O.~Halchenko}}
    \mtitle{Dense mode clustering in brain maps}
    \mwhere{Magnetic Resonance Imaging, 25(9):1249-1262, 2007}

  \item
    \mauthors{\textbf{Y.O.~Halchenko}, S.J.~Hanson, B.A.~Pearlmutter}
    \mtitle{Multimodal Integration: fMRI, MRI, EEG, MEG (Chapter 8)}
    \mwhere{Advanced Image Processing in Magnetic Resonance Imaging,
      Dekker, book series on Signal Processing and Communications, p. 223-265
      ISBN 0824725425, 2005}

  \item
     \mauthors{\textbf{Y.O.~Halchenko}, B.A.~Pearlmutter, S.J.~Hanson, A.~Zaimi}
     \mtitle{Fusion of Functional Brain Imaging Modalities via Linear Programming}
     \mwhere{Presented at NFSI-2003. Chiety Italy September 2003}

  \item
     \mauthors{L.I.~Timchenko, Y.F.~Kutaev, A.A.~Gertsiy, \textbf{Y.O.~Halchenko}}
     \mtitle{Method for image coordinate definition on extended laser paths}
     \mwhere{Optoelectronic and Hybrid Optical/Digital Systems for Image and Signal Processing, Published June 2000,  Volume 4148-19}

  \item
     \mauthors{L.I.~Timchenko, Y.F.~Kutaev, A.A.~Gertsiy, \textbf{Y.O.~Halchenko},
     M.A.~Grudin}
     \mtitle{Approach to parallel-hierarchical network learning for real-time image sequence recognition}
     \mwhere{The International Symposium on Intelligent Systems and Advanced Manufacturing, 19-22 September 1999, Massachusetts USA. Volume 3836-09}

   \item
     \mauthors{L.I.~Timchenco, Y.~Kutaev, A.~Gertsiy, L.~Zagoruiko, \textbf{Y.O.~Halchenko}}
     \mtitle{Pre-processing of extended laser path images}
     \mwhere{Industrial Lasers and Inspection, EOS/SPIE International Symposium. Munich, 14-18 June 1999. Volume 3827-26}

   \item
     \mauthors{L.I.~Tymchenko, J.~Scorukova, S.~Markov, \textbf{Y.O.~Halchenko}}
     \mtitle{Image Segmentation on the basis of spatial connected features}
     \mwhere{Visnyk VSTU, No. 4, pp. 39-43, Ukraine, in Ukrainian, 1998}

   \item
     \mauthors{T.B.~Martinyuk, A.V.~Kogemiako, \textbf{Y.O.~Halchenko}}
     \mtitle{The model of associative processor for numerical data sorting}
     \mwhere{ Visnyk VSTU. No. 2, pp. 19-23, Ukraine, in Ukrainian, 1997}

   \item
     \mauthors{L.I.~Tymchenko, J.~Scorukova, J.~Kutaev, S.~Markov, T.~Martynuk, \textbf{Y.O.~Halchenko}}
     \mtitle{Method Spatial Connected Segmentation of Images}
     \mwhere{The Third All-Ukrainian International Conference Ukrobraz, Kijiv, Ukraine, November 26-30, 1996}
 \end{itemize}

\section{Recent Talks}

 \begin{itemize}

 \item
   \mauthors{\textbf{Y.O.~Halchenko}, M.~Hanke and J.V.~Haxby}
   \mtitle{Multivariate analysis strategies of neuroimaging data in PyMVPA}
   \mwhere{Annual Meeting of Society for NeuroScience, Washington DC,  USA 2011}
%     \url{http://penta.debconf.org/dc10_schedule/events/571.en.html}

 \item
   \mauthors{\textbf{Y.O.~Halchenko} and M.~Hanke}
   \mtitle{The virtues and sins of PyMVPA}
   \mwhere{EuroScipy satellite ``Python in Neuroscience'', Paris, France, 2011}


 \item
   \mauthors{\textbf{Y.O.~Halchenko}}
   \mtitle{$\pi$'s in Debian or Scientific Debian: NumPy, SciPy and beyond}
   \mwhere{EuroScipy, Paris, France, 2011
     \url{http://www.euroscipy.org/talk/4379}}

 \item
   \mauthors{M.~Hanke and \textbf{Y.O.~Halchenko}}
   \mtitle{Debian: The ultimate platform for neuroimaging
     research}
   \mwhere{DebConf10, New York, USA 2010,
     \url{http://penta.debconf.org/dc10_schedule/events/571.en.html}}


% \item
%   \mauthors{M.~Hanke, \textbf{Y.O.~Halchenko}}
%   \mtitle{PyMVPA: A Python toolbox for machine-learning-based fMRI data analysis}
%   \mwhere{PyMVPA Workshop, Dartmouth College, February 2010}
%
% \item
%   \mauthors{\textbf{Y.O.~Halchenko}, M.~Hanke}
%   \mtitle{An ecosystem of neuroimaging, statistical learning,
%     and open-source software to make research more efficient, more open,
%     and more fun}
%   \mwhere{Dartmouth College, November 2009}
%
% \item
%   \mauthors{\textbf{Y.O.~Halchenko}, M.~Hanke}
%   \mtitle{Reliable Decoding of Neural Data}
%   \mwhere{Berkeley, March 2009}
%
% \item
%   \mauthors{\textbf{Y.O.~Halchenko}, M.~Hanke}
%   \mtitle{PyMVPA: Fathom Brain Function through
%     Multivariate Pattern Analysis}
%   \mwhere{University of Hawaii at Manoa, March 2009}
%
 \end{itemize}

\section{Recent Poster Presentations }

\begin{itemize}
 \item
   \mauthors{M.~Hanke, \textbf{Y.O.~Halchenko} and J.V.~Haxby}
   \mtitle{NeuroDebian: versatile platform for brain imaging research}
   \mwhere{Annual Meeting of the Organization for Human Brain Mapping, 2011}

 \item
   \mauthors{M.~Hanke, \textbf{Y.O.~Halchenko}, J.S.C.~Guntupalli,
     A.C.~Connolly and J.V.~Haxby}
   \mtitle{Unsupervised brain parcellation from functional neuroimaging data}
   \mwhere{Annual Meeting of the Cognitive Neuroscience Society, 2011}

 \item
   \mauthors{S.V.~Fogelson, P.J.~Kohler, M.~Hanke, \textbf{Y.O.~Halchenko}, J.V.~Haxby,
     R.H.~Granger and P.U.~Tse}
   \mtitle{STMVPA: Spatiotemporal
     multivariate pattern analysis permits fine- grained visual
     categorization}
   \mwhere{Annual meeting of the Vision Sciences Society, 2011}

 \item
   \mauthors{\textbf{Y.O.~Halchenko}, M.~Hanke, J.V.~Haxby,
     S.~Pollmann, R.D.~Raizada}
   \mtitle{Having trouble getting your Nature paper? Maybe you are not
     using the right tools?}
   \mwhere{Annual Meeting of Society for NeuroScience, USA 2011}

%  \item
%    \mauthors{S.S.~Ghosh, C.D.~Burns, D.~Clark, K.~Gorgolewski,
%        \textbf{Y.O.~Halchenko}, C.~Madison, R.F.~Tungaraza,
%        K.J.~Millman}
%    \mtitle{Nipype: Opensource platform for unified and
%      replicable interaction with existing neuroimaging tools}
%    \mwhere{Annual Meeting of the Organization for Human Brain Mapping,
%    June 2010}
% 
%  \item
%    \mauthors{\textbf{Y.O.~Halchenko}, M.~Hanke, J.V.~Haxby, S.J.~Hanson, S.~Pollmann}
%    \mtitle{Neural activity localization by predictive mapping between imaging modalities}
%    \mwhere{Cognitive Neuroscience Society Annual Meeting, March 2010}
% 
%  \item
%    \mauthors{M.~Hanke, \textbf{Y.O.~Halchenko}, J.V.~Haxby, S.J.~Hanson, S.~Pollmann}
%    \mtitle{Improving efficiency in cognitive neuroscience research with NeuroDebian}
%    \mwhere{Cognitive Neuroscience Society Annual Meeting, March 2010}

\end{itemize}

\section{Professional Activities}
\begin{itemize}
\item Active reviewer for IEEE Transactions on Signal Processing,
  Neural Computation, Neuroimage, and Neurocomputing
%\item Active reviewed under supervision of the advisor for
%  Neuroreport, Neuroimage, NIPS, etc.
\item Active mentor for new Debian contributors
\end{itemize}


\section{Languages}
 Fluent in Russian, Ukrainian and English.

%\pagebreak
 \section{References}

 \vspace{0em}
  \begin{multicols}{2}
 {\small
 %   Dr. Barak A. Pearlmutter, Assistant Professor\\
 %   Department of Computer Science \\
 %   Farris Engineering Center \\
 %   University of New Mexico \\
 %   Albuquerque, NM 87131 \\
 %   Tel: (505) 277-9738 office \\
 %   Tel: (505) 277-1592 lab \\
 %   \url{bap@cs.unm.edu} \\
%    Department of Computer Science \\
%    FEC 157 \\
%    University of New Mexico \\
%    Albuquerque, NM  87131 \\
%    Tel: [505] 277-3112 (office) \\
%    Fax: [505] 277-6927 \\
%    \url{mailto: bap@cs.unm.edu} \\
    Prof. Barak A. Pearlmutter \\
    Hamilton Institute \\
    National University of Ireland, Maynooth \\
    Maynooth, Co. Kildare, \\
    Ireland \\
    Tel: +353 1 708-6394\\
    Fax: +353 1 708-6269\\
    \url{barak@cs.may.ie} \\
    Prof. Stephen J. Hanson \\
%    Department Chair \\
    Psychology Department \\
    Rutgers University, \\
    Smith Hall, 101 Warren Str, \\
    Newark, NJ 07102-1811 \\
    Tel: +1 973 353-5440 \\
    Fax: +1 973 353-1171 \\
    \url{jose@psychology.rutgers.edu}
 }
 \end{multicols}
%\begin{multicols}{1}
\vspace{-1em}
{\small
Prof. James V. Haxby \\
Director of Center for Cognitive Neuroscience \\
Department of Psychological and Brain Sciences \\
Dartmouth College, \\
Moore Hall, Hinman Box 6207 \\
Hanover, NH 03755 \\
Tel: +1 603 646-3181 \\
Fax: +1 603 646-1419 \\
\url{james.v.haxby@dartmouth.edu} \\
}
%end{multicols}
% Additional references available upon request.



\end{resume}
\end{document}
